The supernova-regulated ISM - III. Magnetic fields in the multi-phase gas

### 2015-03-10 paper.tex

\begin{figure*}
  \vspace{0cm}
  \centering
\hspace*{0cm} \includegraphics[width=\linewidth]{snapshot1.png}
\hspace*{0cm} \caption{3D rendering of the field lines of the mean magnetic field. The white lines are field lines seeded along a regular grid on the $xz$-plane at $y\approx-0.5$ kpc. 
  \label{fig:fld_lines}}
  \end{figure*}
\begin{figure}
\centering
\includegraphics[width=\linewidth]{sline_vs_fld1.pdf}
\caption{PDFs of entropy (blue), $s$, log density (red), $\log(n)$, and log temperature (green), $\log(T)$, along field lines (solid) and straight lines (dashed).}
\label{fig:pdfs_mean}
\end{figure}
%-----------------------------------------------------------------------------

@@

\footnote{CAN: please add snapshot1new.png to the repository}

@@

%\hspace*{0cm} \includegraphics[scale=0.35]{fig/snapshot1new.png}

@@

\includegraphics[width=\linewidth]{fig/snapshot1.png}
%\includegraphics[width=\linewidth]{snapshot0_entropy.pdf}

@@

\footnote{CAN: please add snapshot0\_entropy.pdf to the repository} 

@@

\footnote{CAN: please add ent\_pdfs.pdf and prob\_corrs\_all.pdf to the repository} 

@@

\subfigure[]{\includegraphics[width=0.49\linewidth]{fig/snapshot1.png}}
%\subfigure[]{\includegraphics[width=0.49\linewidth]{ent_pdfs.pdf}}
%\subfigure[]{\includegraphics[width=0.49\linewidth]{prob_corrs_all.pdf}}

@@

%-----------------------------------------------------------------------------
\subsection{Curve fitting for PDFs of entropy}
%-----------------------------------------------------------------------------

>>>>

\begin{figure*}
  \vspace{0cm}
  \centering
\hspace*{0cm} \includegraphics[width=\linewidth]{snapshot1.png}
%\hspace*{0cm} \includegraphics[width=\linewidth]{snapshot1new.png}
\hspace*{0cm} \caption{3D rendering of the field lines of the mean magnetic field. The white lines are field lines seeded along a regular grid on the $xz$-plane at $y\approx-0.5$ kpc. 
  \label{fig:fld_lines}}
  \end{figure*}
\begin{figure}
\centering
\includegraphics[width=\linewidth]{sline_vs_fld1.pdf}
\caption{PDFs of entropy (blue), $s$, log density (red), $\log(n)$, and log temperature (green), $\log(T)$, along field lines (solid) and straight lines (dashed).}
\label{fig:pdfs_mean}
\end{figure}
%-----------------------------------------------------------------------------

@@

@@

@@

\includegraphics[width=\linewidth]{snapshot0_entropy.pdf}

@@

@@

@@

\subfigure[]{\includegraphics[width=0.49\linewidth]{ent_pdfs.pdf}}
\subfigure[]{\includegraphics[width=0.49\linewidth]{prob_corrs_all.pdf}}

@@

%-----------------------------------------------------------------------------
\subsection{Curve fitting for PDFs of entropy}
%-----------------------------------------------------------------------------
\subsection{Correlation lengths of the magnetic fields}
\begin{table}[H]
 \centering
 %\begin{minipage}{180mm}
  \caption{Correlation lengths for the total, mean and random magnetic field in kpc.}
  \label{table:mean_probs}
 % \begin{tabular*}{@{}c c c @{}}{\linewidth}{@{\extracolsep{\fill}}p{0.3\linewidth}p{0.3\linewidth}p{0.3\linewidth}@{}}
\begin{tabular*}{\linewidth}{p{0.20\linewidth}p{0.20\linewidth}p{0.2\linewidth}p{0.2\linewidth}@{}}
  \hline
Correlation length &Total magnetic field& Mean magnetic field& Random magnetic field \\
 \hline
\\
$C$&$0.711$&$0.700$&$0.241$ \\
$C_x$& $0.061$&$0.045$&$0.065$   \\
$C_y$&$0.380$ & $0.0.376$&$0.090$    \\
$C_z$&0.124&$0.084$&$0.105$\\
\hline
\end{tabular*}
%\end{minipage}
\end{table}
